Commit Rater

### 2015-08-26 presentations/paper/methodology.tex
ÂDescribe commit-level analysis

>>>>

\subsubsection{Commit-level}
\label{subs:Commit-level}
Although looking at the results of a single commit might be interesting for debugging the criteria tests, there are not many options for analysis. The percentage of passed tests could serve as a rating for the commit, where 100\% means having passed all tests, but no further conclusions could be drawn from this level. Therefore, we did not concern ourselves with this level.
